AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-09-28 Paper/main.tex
paper
9-28 cnn

Based on the categorization above, we assume that method in spatial domain and in temporal domain are heterogeneous, 
which can satisfy the diversity premise of ensemble learning. 
Based on assumption above and ensemble learning, we follow the stacking strategy to develop AttCRISPR 
which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
Further, we use attention mechanisms in both spatial and temporal domain respectively to enhance the interpretability of AttCRISPR.

@@

>>>>

Based on the categorization above, we assume that method in spatial domain and in temporal domain are heterogeneous, 
which can satisfy the diversity premise of ensemble learning. 
Based on assumption above and ensemble learning, we follow the stacking strategy to develop AttCRISPR 
which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
Further, we apply attention mechanisms in both spatial and temporal domain respectively to enhance the interpretability of AttCRISPR.

@@

\begin{figure}[!tpb]%figure2
    \centerline{\includegraphics[scale=0.15]{newcnn.png}}
    \caption{Two categories of the deep learning models used in sgRNA related task. 
    (a) Model work in spatial domain. (b) Model work in temporal domain.}\label{fig:02}
\end{figure}
As Figure~1\vphantom{\ref{fig:02}} show,
